A Warm Sub-Neptune Transiting a Solar Twin in TESS

### 2019-10-07 paper/ms.tex

\include{preamble}
\newcommand{\hoststar}{\acronym{HIP}\ 96160\xspace}
\newcommand{\plname}{\acronym{HIP}\ 96160b\xspace}
\newcommand{\plmass}{$13.1 \pm 5.0\ \textrm{M}_{E}$\xspace}
\newcommand{\plradius}{$3.41 \pm 0.01\ \textrm{R}_{E}$\xspace}
\newcommand{\stmass}{$1.0 \pm x\ \textrm{M}_{\odot}$\xspace}
\newcommand{\stradius}{$1.0 \pm x\ \textrm{R}_{\odot}$\xspace}

@@

@@

@@

>>>>

\include{preamble}
\graphicspath{ {./figures/} }
\newcommand{\hoststar}{\acronym{HIP}\ 96160\xspace}
\newcommand{\plname}{\acronym{HIP}\ 96160b\xspace}
\newcommand{\plmass}{$13.1 \pm 5.0\ \textrm{M}_{E}$\xspace}
\newcommand{\plradius}{$3.41 \pm 0.01\ \textrm{R}_{E}$\xspace}
\newcommand{\stmass}{$1.0 \pm x\ \textrm{M}_{\odot}$\xspace}
\newcommand{\stradius}{$1.0 \pm x\ \textrm{R}_{\odot}$\xspace}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{lightcurve.pdf}
    \caption{Photometric lightcurve of \hoststar as observed by \TESS in Sector 13. The \TESS data were fit with a Gaussian Process model (top panel) as a means of detrending. A transit model was then fit (middle panel), leaving a featureless white-noise lightcurve in the residuals (bottom panel).}
    \label{fig:lightcurve}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{periodograms.pdf}
    \caption{Lomb-Scargle periodograms of the \HARPS \RV, BIS, FWHM, and \shk timeseries measurements. Horizontal lines indicate the 5\%, 1\%, and 0.1\% false alarm probability levels. Vertical red lines mark the period of the \TESS-detected planet. The \RV, BIS, and FWHM measurements used here have been corrected for the \HARPS upgrade offset.}
    \label{fig:periodograms}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{periodogram_resids1.pdf}
    \caption{Lomb-Scargle periodogram of the \RV residuals after subtracting the best-fit no-planet model consisting of a quadratic trend, a linear correlation with FWHM, and an instrumental offset after the time of the \HARPS upgrade.}
    \label{fig:periodogram_resids1}
\end{figure}
